\name{}: machine learning over interaction networks and ontology-based background knowledge predicts drug--target interactions

### 2021-07-13 paper/main.tex
.

As the target-based predictive power of \name{} improves significantly
over other methods, we utilized our model to predict novel drug
classes for protein families. We therefore collected the 2nd level ATC
(Anatomical Therapeutic Chemical) groups for each drug and all
InterPro \cite{Interpro2020} top-level families for each
protein. Utilizing the STITCH interactions, we followed a protein
split within each InterPro family by predicting over all available
drugs. We eventually normalized the number of novel interactions per
class by the amount of proteins within the respective family. A
heatmap showing the results of this analysis can be found in
Supplementary Figure 5. \dots \todo{Roberts class analysis}.

Most of novel predictions made by \name{} are for antineoplastic
agents targeting proteins belonging to the Zinc finger, LIM-type
family ({\tt IPR001781}).

>>>>

As the target-based predictive power of \name{} improves significantly
over other methods, we utilized our model to predict novel drug
classes for protein families. We therefore collected the 2nd level ATC
(Anatomical Therapeutic Chemical) groups for each drug and all
InterPro \cite{Interpro2020} top-level families for each
protein. Utilizing the STITCH interactions, we followed a protein
split within each InterPro family by predicting over all available
drugs. We eventually normalized the number of novel interactions per
class by the amount of proteins within the respective family. A
heatmap showing the results of this analysis can be found in
Supplementary Figure 5. \name{} predicts novel candidate drug--target
interactions for a broad range of ATC categories as well as protein
families.

For example, ATC group A07 (Antidiarrheals) has relatively few
approved drugs in total (Supplementary Figure 6), but \name{} predicts
several candidate targets from proteins with a PHD-type zinc finger
domain ({\tt IPR001965}). For example, the drug mesalazine, used to
treat inflammatory bowel disease but with an apoptosis-inducing and
chemopreventative effect in colon cancer \cite{Bus1999, Ishikawa2021};
\name{} predicts mesalazine to interact with five proteins with
PHD-type zinc finger domain: BRPF1, TRIM33, BAZ1A, RSF1, and
DPF2. Overexpression of RSF1 is associated with poor prognosis in
colorectal cancer, and knock-down of RSF1 leads to decrease of cell
proliferation \cite{Liu2012}, indicating that, in addition to its
antiinflammatory effects, mesalazine may act through inhibition of
RSF1 in its chemopreventative effects on colon cancer.
